Unknown

### 2024-04-09 ms/ms.qmd
drafted tbl-models

We fit Bayesian models with MCMC sampling in the probabilistic programming language *Stan* [@stan_development_team_stan_2023]. We used CmdStan version `r fit_aa$version$cmdstan` and **cmdstanr** version `r fit_aa$version$cmdstanr` [@gabry_cmdstanr_2023] to interface with *R* version `r getRversion()` [@r_core_team_r:_2023]. We sampled the posterior distribution from `r dim_fit_aa[2]` chains with `r dim_fit_aa[1]` iterations each after `r dim_fit_aa[1]` warmup iterations per chain. We estimated parameters and confidence intervals as the median and 95% quantile intervals of the posterior, respectively.

@@

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS?
- TABLE SUMMARIZING PARAMETERS

>>>>

We fit Bayesian models with MCMC sampling in the probabilistic programming language *Stan* [@stan_development_team_stan_2023]. We used CmdStan version `r fit_aa$version$cmdstan` and **cmdstanr** version `r fit_aa$version$cmdstanr` [@gabry_cmdstanr_2023] to interface with *R* version `r getRversion()` [@r_core_team_r:_2023]. We sampled the posterior distribution from `r dim_fit_aa[2]` chains with `r dim_fit_aa[1]` iterations each after `r dim_fit_aa[1]` warmup iterations per chain. We estimated parameters and confidence intervals as the median and 95% quantile intervals of the posterior, respectively. 
#### *Stan* models

- high level overview of differences among models \autoref{tbl-models}
- next section describes common elements of all models and additional details about parameters

```{r, models, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-models
#| tbl-cap: "Summary of differences among competing models of how \\aax{} varies with light intensity, light treatment, and among accessions as a function of native \\ppfd. The models are numbered from simpler to more complex. All models include fixed effects of light intensity and light treatment; some models include interactions between. All models include a phylogenetic random effect of accession on \\aax; some models include varying effects of light intensity and light treatment among accessions. The last column indicates the accession-level \\aax{} variable we used as a response to native \\ppfd."

tribble(
    ~"Model", ~"Fixed effects", ~"Phylogenetic random effects", ~"Response to native \\ppfd",
    "1", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{0, \\text{acc}}$",
    "1", "light treatment", "", "",
    "2", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{0, \\text{acc}}$",
    "2", "light treatment", "", "",
    "2", "intensity $\\times$ treatment", "", "",
    "3", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{2000, \\text{acc}}$",
    "3", "light treatment", "varying effect of high light intensity among accessions", "",
    "4", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{\\text{sun, acc}}$",
    "4", "light treatment", "varying effect of sun treatment among accessions", "",
    "5", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{2000, \\text{sun, acc}}$",
    "5", "light treatment", "varying effect of high light intensity among accessions", "",
    "5", "intensity $\\times$ treatment", "varying effect of sun treatment among accessions", ""
  ) |>
  knitr::kable(
    format = "latex",
    align = c("c", "l", "l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = FALSE
  ) |>
    kableExtra::collapse_rows(columns = 1, latex_hline = "major", row_group_label_position = "first") |>
  kableExtra::column_spec(1, width = "0.3in") |>
  kableExtra::column_spec(2, width = "1.3in") |>
  kableExtra::column_spec(3, width = "3.4in") |>
  kableExtra::column_spec(4, width = "1in")

@@

### 2024-04-09 ms/ms.tex
drafted tbl-models

We fit Bayesian models with MCMC sampling in the probabilistic
programming language \emph{Stan} (\emph{11}). We used CmdStan version
2.33.1 and \textbf{cmdstanr} version 0.7.1 (\emph{12}) to interface with
\emph{R} version 4.3.2 (\emph{13}). We sampled the posterior
distribution from 4 chains with 1000 iterations each after 1000 warmup
iterations per chain. We estimated parameters and confidence intervals
as the median and 95\% quantile intervals of the posterior,
respectively.

>>>>

We fit Bayesian models with MCMC sampling in the probabilistic
programming language \emph{Stan} (\emph{11}). We used CmdStan version
2.33.1 and \textbf{cmdstanr} version 0.7.1 (\emph{12}) to interface with
\emph{R} version 4.3.2 (\emph{13}). We sampled the posterior
distribution from 4 chains with 1000 iterations each after 1000 warmup
iterations per chain. We estimated parameters and confidence intervals
as the median and 95\% quantile intervals of the posterior,
respectively. \#\#\#\# \emph{Stan} models

\begin{itemize}
\tightlist
\item
  high level overview of differences among models \autoref{tbl-models}
\item
  next section describes common elements of all models and additional
  details about parameters
\end{itemize}

\caption{\label{tbl-models}Summary of differences among competing models
of how \aax{} varies with light intensity, light treatment, and among
accessions as a function of native \ppfd. The models are numbered from
simpler to more complex. All models include fixed effects of light
intensity and light treatment; some models include interactions between.
All models include a phylogenetic random effect of accession on \aax;
some models include varying effects of light intensity and light
treatment among accessions. The last column indicates the
accession-level \aax{} variable we used as a response to native \ppfd.}

\begin{tabular}{>{\centering\arraybackslash}p{0.3in}>{\raggedright\arraybackslash}p{1.3in}>{\raggedright\arraybackslash}p{3.4in}>{\raggedright\arraybackslash}p{1in}}
\toprule
Model & Fixed effects & Phylogenetic random effects & Response to native \ppfd\\
\midrule
1 & light intensity & varying intercept among accessions & $\mathrm{AA}_{0, \text{acc}}$\\

 & light treatment &  & \\
\cmidrule{1-4}
2 & light intensity & varying intercept among accessions & $\mathrm{AA}_{0, \text{acc}}$\\

 & light treatment &  & \\

 & intensity $\times$ treatment &  & \\
\cmidrule{1-4}
3 & light intensity & varying intercept among accessions & $\mathrm{AA}_{2000, \text{acc}}$\\

 & light treatment & varying effect of high light intensity among accessions & \\
\cmidrule{1-4}
4 & light intensity & varying intercept among accessions & $\mathrm{AA}_{\text{sun, acc}}$\\

 & light treatment & varying effect of sun treatment among accessions & \\
\cmidrule{1-4}
5 & light intensity & varying intercept among accessions & $\mathrm{AA}_{2000, \text{sun, acc}}$\\

 & light treatment & varying effect of high light intensity among accessions & \\

 & intensity $\times$ treatment & varying effect of sun treatment among accessions & \\
\bottomrule
\end{tabular}

### 2024-04-09 ms/test.qmd
drafted tbl-models

Manual curation of a data set this size in a principled, consistent manner is not feasible. Therefore, we automated data cleaning using custom *R* scripts. Cleaning is divided into six sequential steps \autoref{tbl-parameters}.

```{r, parameters, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-parameters
#| tbl-cap: "caption"

df_parameters = read_csv("../data/parameters1.csv", col_types = "cccc", n_max = 6)

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("c", "l"),
    booktabs = TRUE,
    escape = FALSE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) #|>
                        # kableExtra::pack_rows("x", 2, 2)

>>>>

blah \autoref{tbl-models}.

```{r, models, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-models
#| tbl-cap: "Summary of differences among competing models of how \\aax{} varies with light intensity, light treatment, and among accessions as a function of native \\ppfd. The models are numbered from simpler to more complex. All models include fixed effects of light intensity and light treatment; some models include interactions between. All models include a phylogenetic random effect of accession on \\aax; some models include varying effects of light intensity and light treatment among accessions. The last column indicates the accession-level \\aax{} variable we used as a response to native \\ppfd."

tribble(
    ~"Model", ~"Fixed effects", ~"Phylogenetic random effects", ~"Response to native \\ppfd",
    "1", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{0, \\text{acc}}$",
    "1", "light treatment", "", "",
    "2", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{0, \\text{acc}}$",
    "2", "light treatment", "", "",
    "2", "intensity $\\times$ treatment", "", "",
    "3", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{2000, \\text{acc}}$",
    "3", "light treatment", "varying effect of high light intensity among accessions", "",
    "4", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{\\text{sun, acc}}$",
    "4", "light treatment", "varying effect of sun treatment among accessions", "",
    "5", "light intensity", "varying intercept among accessions", "$\\mathrm{AA}_{2000, \\text{sun, acc}}$",
    "5", "light treatment", "varying effect of high light intensity among accessions", "",
    "5", "intensity $\\times$ treatment", "varying effect of sun treatment among accessions", ""
  ) |>
  knitr::kable(
    format = "latex",
    align = c("c", "l", "l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = FALSE
  ) |>
    kableExtra::collapse_rows(columns = 1, latex_hline = "major", row_group_label_position = "first") |>
  kableExtra::column_spec(1, width = "0.3in") |>
  kableExtra::column_spec(2, width = "1.3in") |>
  kableExtra::column_spec(3, width = "3.4in") |>
  kableExtra::column_spec(4, width = "1in")
